DRAFT

### 2022-11-01 Draft.Rmd
Update Draft.Rmd
#missing values - data quality overview

---
title: "DRAFT"
author: "Alima Dzhanybaeva"
date: "2022-10-31"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(dplyr)
library(knitr)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
### Table 1.1 shows the main variables, their description and type.
```{r include=FALSE}
variables <- c('hotel_id','accommodation_type', 'addresscountryname', 'weekend', 'holiday',
               'center1distance', 'starrating', 'guestreviewrating', 'price', 'price_night',
               'year', 'month')
info <- c('Hotel ID', 'Type of accomodation', 'Country', 'Flag, if day is a weekend',
          'Flag, if day is a public holiday', 'Distance from main city center',
          'Number of stars', 'User rating average', 'Price in EUR', 'Number of nights',
          'Year (YYYY)', 'Month (MM)')
type <- c('numeric', 'string', 'string', 'binary', 'binary', 'string',
          'numeric', 'string', 'numeric', 'string', 'numeric', 'numeric')
description <- data.frame(variables, info, type)
```
```{r}
kable(description, caption = "Table 1.1 Description of the main variables in the original dataset")
```
## 1.2 Dataset for 7 Central European countries
### For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df <- read.csv('https://osf.io/yzntm/download')
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))

>>>>

---
title: "DRAFT"
author: "Alima Dzhanybaeva"
date: "2022-10-31"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(dplyr)
library(knitr)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
### Table 1.1 shows the main variables, their description and type.
```{r include=FALSE}
variables <- c('hotel_id','accommodation_type', 'addresscountryname', 'weekend', 'holiday',
               'center1distance', 'starrating', 'guestreviewrating', 'price', 'price_night',
               'year', 'month')
info <- c('Hotel ID', 'Type of accomodation', 'Country', 'Flag, if day is a weekend',
          'Flag, if day is a public holiday', 'Distance from main city center',
          'Number of stars', 'User rating average', 'Price in EUR', 'Number of nights',
          'Year (YYYY)', 'Month (MM)')
type <- c('numeric', 'string', 'string', 'binary', 'binary', 'string',
          'numeric', 'string', 'numeric', 'string', 'numeric', 'numeric')
description <- data.frame(variables, info, type)
```
```{r}
kable(description, caption = "Table 1.1 Description of the main variables in the original dataset")
```
### Quality of the dataset - missing values overview

```{r}
df2 %>% 
  skimr::skim_without_charts() 
```

## 1.2 Dataset for 7 Central European countries
### For our analysis we used 7 Central European countries: Czech Republic, Germany, Italy, Hungary, Austria, Poland, Slovakia.
```{r}
df <- read.csv('https://osf.io/yzntm/download')
df2 <- df %>% filter(addresscountryname %in% 
                       c('Czech Republic', 'Germany', 'Italy', 
                         'Hungary', 'Austria', 'Poland', 'Slovakia'))
